---
title: "How to run nnvis"
author: "Tyler J Burns"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Description

This package allows one to understand how a low-dimensional embedding is
representing your data by comparing each cell's k-nearest neighbors in the
original high-dimensional feature space to that of the low dimensional space. 
The can allow for both global and local readouts of shared neighborhoods. 

The example below uses the mouse bone marrow data provided in this dataset. 
I'll start with the pieces. 

```{r}
library(nnvis)

# The cells
samusik_cells

# The markers
samusik_surface_markers

# The lowd embedding
samusik_tsne
```

Now that you know that the data look like, let's run the pipeline. Note that
you can name the columns of your low dimensional embedding whatever you want. 
All that matters is you know what markers to use as input for the original
feature space. 

```{r, message=FALSE}
# Set a few values for k
k_titration <- c(20, 200)

# The wrapper
result <- ComparisonPipeline(orig = samusik_cells, 
                             input.markers = samusik_surface_markers, 
                             lowd = samusik_tsne,
                             k.titration = k_titration)

# What the output looks like
result
```

Notice that the result is a tibble of cells by a KNN sizes. Each element
accordingly is a percentage of shared KNN between original space and 
embedded space for the specified size of K. There are two things you can 
do from here. The first is to do simple statistics on the global output. 

```{r}
library(ggplot2)

# Histograms
qplot(result[[2]]) + geom_histogram()

# Mean
apply(result, 2, mean)

# SD
apply(result, 2, sd)

```

I don't know about you, but this was quite a bit less than I thought it would
be when I first saw these numbers. The obvious question about locality leads
me to the next thing you can do with this: visualize these percentages 
directly on your low dimensional embedding to see what regions of the map 
are better preserved. 

```{r}

# For K = 20
qplot(samusik_tsne[[1]], 
      samusik_tsne[[2]], 
      color = result[[1]],
      xlab = "bh-SNE1",
      ylab = "bh-SNE2") + 
  geom_point(size = 0.1, stroke = 0, shape = 16) +
  scale_color_gradientn(colors = c("black", "yellow")) + 
  theme(legend.title=element_blank())

# For K = 200
qplot(samusik_tsne[[1]], 
      samusik_tsne[[2]], 
      color = result[[2]],
      xlab = "bh-SNE1",
      ylab = "bh-SNE2") + 
  geom_point(size = 0.1, stroke = 0, shape = 16) +
  scale_color_gradientn(colors = c("black", "yellow")) + 
  theme(legend.title=element_blank())

```

The color on this t-SNE map corresponds to the shared KNN. You can see that there are indeed local differences across the map, with the larger subsets being less well preserved. I would recommend exporting the data and visualizing on external
software like FlowJo or Cytobank, as follows. 

```{r, eval = FALSE}
# Bind everything into a large tibble
final <- bind_cols(samusik_cells, samusik_tsne, result)

# Export to CSV for import into external software.
write.csv("samusik_nn_compare.csv")
```

