---
title: "How to run nnvis"
author: "Tyler J Burns"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Description

This package allows one to understand how a low-dimensional embedding is
representing your data by comparing each cell's k-nearest neighbors in the
original high-dimensional feature space to that of the low dimensional space. 
The can allow for both global and local readouts of shared neighborhoods. 

The example below uses the mouse bone marrow data provided in this dataset. 
I'll start with the pieces. 

```{r}
library(nnvis)

# The cells
samusik_cells

# The markers
samusik_surface_markers

# The lowd embedding
samusik_tsne
```

Now that you know that the data look like, let's run the pipeline. Note that
you can name the columns of your low dimensional embedding whatever you want. 
All that matters is you know what markers to use as input for the original
feature space. 

```{r, message=FALSE}
# Set a few values for k
k_titration <- c(10, 100)

# The wrapper
result <- ComparisonPipeline(orig = samusik_cells, 
                             input.markers = samusik_surface_markers, 
                             lowd = samusik_tsne,
                             k.titration = k_titration)

# What the output looks like
result
```
